Calculate FD

### 2020-08-24 analysis/calc_fd.Rmd
Incorporate abundance into FD calculations and scale using the z score

```{r}
library(tidyverse)
library(furrr)
library(FD)
```

@@

FD function:
```{r}
load(here::here("data", "biotime_traits.rda"))

@@

  species_mat <- data %>%
    select(year, id) %>% 
    distinct() %>%
    arrange(year, id) %>%
    mutate(present = 1) %>%
    spread(id, value = present, fill = 0) %>%
    select(-year)

@@

  trait_mat <- data %>%
    select(-c(taxa, record_id, day, month, year, sample_desc, id_species, 
              latitude, longitude, sum_abundance, sum_biomass, traitName, 
              biotimeName, scientificName)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(.)) > 1) %>% #remove columns that have the same value for all columns
    mutate_at(vars(-id, -ends_with("5cat")), list(~scales::rescale(.,to=c(0, 1)))) %>% #rescale variables
    arrange(id) %>%
    column_to_rownames("id")

>>>>

```{r}
library(tidyverse)
library(furrr)
library(FD)
library(biodivTS)
```

@@

FD function:
```{r}
biotime_traits <- pins::pin_get("biotime-traits", board = "github")

@@

  species_mat <- data %>%
    select(year, id, sum_abundance) %>% 
    distinct() %>%
    arrange(year, id) %>%
    spread(id, value = sum_abundance, fill = 0) %>%
    select(-year)

@@

  trait_mat <- data %>%
    select(-c(taxa, record_id, day, month, year, sample_desc, id_species, 
              latitude, longitude, sum_abundance, sum_biomass, traitName, 
              biotimeName, scientificName)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(na.omit(.))) > 1) #remove columns that have the same value for all columns

  #get binary variables so they can be excluded from rescaling 
  bin_vars <- map(trait_mat, ~ all(na.omit(.) %in% 0:1))

  trait_mat <- trait_mat %>%
    mutate_at(vars(-c(id, names(bin_vars[bin_vars == TRUE])), -ends_with("5cat")), 
              list(~as.numeric(scale(.)))) %>% #rescale variables, not binary or categorical
    arrange(id) %>%
    column_to_rownames("id")
